### 2023-12-29 sections/4-results.tex
fix reference

@@

In contrast with the results on the ANN Benchmark datasets reported above, with the Random dataset, as seen in Figure~\ref{fig:results:random-scaling}, we observe that the three CAKES algorithms are the slowest out of all algorithms, at all cardinalities.
As with the real datasets, HNSW and ANNOY are the fastest algorithms, and CAKES exhibits perfect recall at all cardinalities.
HNSW and ANNOY exhibit \emph{much} lower recall on this random dataset than on any of the ANN benchmark datasets;
in particular, with a multiplier of 1, HNSW and ANNOY have recall as low as 0.060 and 0.028 respectively, as reported in Table~\ref{tab:results:random}.

@@

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/fashion-mnist-knn-10.png}
        \subcaption{Fashion-Mnist for $k=10$.}
        \label{fig:results:fashion-mnist-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/glove-25-knn-10.png}
        \subcaption{Glove-25 for $k=10$.}
        \label{fig:results:glove-25-scaling}
    \end{subfigure}%
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/sift-knn-10.png}
        \subcaption{Sift for $k=10$.}
        \label{fig:results:sift-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/radio-ml-knn-10.png}
        \subcaption{RadioML for $k=10$ at SnR = 10dB.}
        \label{fig:results:radioml-scaling}
    \end{subfigure}%
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/silva-knn-10.png}
        \subcaption{Silva for $k=10$.}
        \label{fig:results:silva-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/random-knn-10.png}
        \subcaption{A random dataset for $k=10$.}
        \label{fig:results:random-scaling}
    \end{subfigure}%
    \caption{Throughput across six datasets, including a randomly-generated dataset.
    In each plot, the horizontal axis represents increasing cardinality of the dataset, while the vertical axis represents the throughput in queries per second (higher is better).
    For some algorithms, we were not able to take measurements for each cardinality because the index-building required more RAM than was available (i.e. more then 512GB).}
    \label{fig:results:scaling-plots}
\end{figure}

>>>>

{\color{red} \sout{TODO: Eliminate all non-red TODOs.}}

@@

In contrast with the results on the ANN Benchmark datasets reported above, with the Random dataset, as seen in Figure~\ref{fig:results:random-scaling}, we observe that the three CAKES algorithms are the slowest out of all algorithms, at all cardinalities.
As with the real datasets, HNSW and ANNOY are the fastest algorithms, and CAKES exhibits perfect recall at all cardinalities.
HNSW and ANNOY exhibit \emph{much} lower recall on this random dataset than on any of the ANN benchmark datasets;
in particular, with a multiplier of 1, HNSW and ANNOY have recall as low as 0.060 and 0.028 respectively, as reported in Table~\ref{tab:results:qps-and-recall}.

@@

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/fashion-mnist-knn-10.png}
        \subcaption{Fashion-Mnist for $k=10$.}
        \label{fig:results:fashion-mnist-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/glove-25-knn-10.png}
        \subcaption{Glove-25 for $k=10$.}
        \label{fig:results:glove-25-scaling}
    \end{subfigure}%
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/sift-knn-10.png}
        \subcaption{Sift for $k=10$.}
        \label{fig:results:sift-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/radio-ml-knn-10.png}
        \subcaption{RadioML for $k=10$ at SnR = 10dB.}
        \label{fig:results:radioml-scaling}
    \end{subfigure}%
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/silva-knn-10.png}
        \subcaption{Silva for $k=10$.}
        \label{fig:results:silva-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/random-knn-10.png}
        \subcaption{A random dataset for $k=10$.}
        \label{fig:results:random-scaling}
    \end{subfigure}%
    \caption{Throughput across six datasets, including a randomly-generated dataset.
    In each plot, the horizontal axis represents increasing cardinality of the dataset, while the vertical axis represents the throughput in queries per second (higher is better). Note that for RadioML, all three algorithms performed nearly identically, so distinct plotlines are not visible.
    For some algorithms, we were not able to take measurements for each cardinality because the index-building required more RAM than was available (i.e. more then 512GB).}
    \label{fig:results:scaling-plots}
\end{figure}
